Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-21 paper/paper.tex
introduction to inference algorithms

An inference algorithm is an implementation of the (ad-hoc)
polymorphic function \texttt{infer} declared as Clojure's multimethod
in the \texttt{anglican.inference} namespace. The
function accepts an algorithm identifier, a query --- the
probabilistic program in which to perform the inference, an
initial value for the query, and optional algorithm parameters.

>>>>

A probabilistic program in Anglican may look almost like a
Clojure program, however the purpose of executing a
probabilistic program is different from that of a `regular'
program: instead of producing the result of a single execution,
a probabilistic program computes, exactly or approximately, the
distribution from which execution results are drawn.  Computing
the distribution is facilitated by an inference algorithm.

Probabilistic programming system Anglican provides a variety of
approximate inference algorithms. Ideally, Anglican should
automatically choose the most appropriate algorithm for each
probabilistic program. In practice, selecting an inference
algorithm, or a combination thereof, is still a challenging
task, and program structure, intended use of the computation
results, performance, approximation accuracy, and other factors
must be taken into consideration. New algorithms are being
developed and added to Anglican~\cite{TMP+15,MPT+16,RNL+2016},
as a part of ongoing research.

In the implementation of Anglican, inference algorithms are
instantiations of the (ad-hoc) polymorphic function
\texttt{infer} declared as Clojure's multimethod in the
\texttt{anglican.{\linebreak[0]}inference} namespace. The function accepts an
algorithm identifier, a query --- the probabilistic program in
which to perform the inference, an initial value for the query,
and optional algorithm parameters.
